---
title: "Cue validity / prev regression and RSA comparison"
output: html_notebook
---

```{r preamble}
library(langcog)
library(tidyr)
library(dplyr)
library(data.table)
library(coda)
library(knitr)
library(ggthemes)
library(rwebppl)
library(jsonlite)
library(ggmcmc)
theme_set(theme_few())
estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
project.path <- "~/Documents/research/generics-paper/"
data.path <- "data/familiar_generics/"
model.path <- "models/generics/alternative_models/"
wp.pkg.path <- paste(project.path, "models/generics/node_modules/utils/", sep = "")
betaMean = function(a, b){
  return ( a / (a + b ))
}

betaSDev = function(a, b){
  return( sqrt ( ( a * b) / ( ( a + b ) ^ 2 * (a + b + 1) ) ) ) 
}
```

### Questions

1. Does empirical cue validity corespond to cue validity derived from the prevalence prior?
2. Can we tease apart a cue validity + prevalence regression (speaker) model from the RSA speaker model?


```{r}
d.cv <- read.csv(paste(project.path, data.path, "cue-validity-1-trials.csv", sep = ""))

d.target.items <- fromJSON(paste(project.path, data.path, "originalStims.json", sep = "")) %>%
  mutate(item = paste(category, property))

d.cv.targets <- d.cv %>%
  mutate(property = gsub("&quotechar", "'", property), 
         item = paste(category, property)) %>%
  filter( item %in% d.target.items$item)

d.cv.out <- left_join(d.cv.targets %>%
                        #mutate(property = gsub("'", "", property)) %>%
                        select(-item),
                      d.target.items) %>%
  mutate(Property = gsub("'", "", Property)) %>%
  select(workerid, trial_num, Category, Property, response)
```


```{r}
d.prev <- read.csv(paste(project.path, data.path,
                       "naturalGenerics-prior-trials-n57.csv", sep = ""))

properties <- levels(d.prev$Property)

d.prev <- d.prev %>%
  mutate(roundedPrevalence = prevalence / 100,
         roundedPrevalence = ifelse(roundedPrevalence < 0.01, 0.01, 
                                    ifelse(roundedPrevalence> 0.99, 0.99, roundedPrevalence)))
```

```{r}
d.tj <- read.csv(paste(project.path, data.path,
                       "naturalGenerics-trials-formatted.csv", sep = "")) %>%
  rowwise() %>%
  mutate(response = ifelse(response == "agree-key", 1, 0))
```


#### Prevalence prior

```{r wpplHelpers}
wpHelpers <- '
var betaShape = function(p){
  return {a: p.g * p.d, b: (1-p.g) * p.d}
};
'
```


```{r prevalencePriorModel}
prevalencePrior <- '
var model = function(){
  var theta = uniformDrift({a: 0, b: 1, width: 0.2})
  var betaParams = betaShape({
    g: uniformDrift({a: 0, b: 1, width: 0.2}),
    d: uniformDrift({a: 0, b: 60, width: 10})
  })

  var nullParams = {
    a:1, b: uniformDrift({a: 0, b: 100, width: 10})
  }

  mapData({data: data}, function(d){
	 factor(
		 util.logsumexp([
				Math.log(theta) + Beta(betaParams).score(d.roundedPrevalence),
				Math.log(1-theta) + Beta(nullParams).score(d.roundedPrevalence)
			]))
  })

  return {theta: theta, a: betaParams.a, b: betaParams.b, nullB: nullParams.b}
}
'
```

```{r runPriorModel}
n_samples = 1000
burn = n_samples

wp.post.summary <- data.frame()

for (p in properties){
  wp.post <- webppl(program_code = paste(wpHelpers, prevalencePrior, sep = "\n"),
       model_var = "model",
       inference_opts = list(method = "MCMC", samples = n_samples, burn = burn, verbose = TRUE),
       data = d.prev %>% filter(Property == p),
       data_var = "data",
       chains = 3, cores = 3)
  
  wp.post.summary <- bind_rows(
    wp.post.summary,
    wp.post %>%
      group_by(Parameter) %>%
      summarize(MAP = estimate_mode(value), cred_upper = hdi_upper(value), cred_lower = hdi_lower(value)) %>%
      mutate(Property = p)
  )
  
  print(p)
}
save(wp.post.summary, file = paste(project.path, model.path, "results/prevPriorParams_mcmc1k_burn1k.Rdata", sep = ""))
```

##### Pseudocounts

```{r scatter1}
wp.post.summary %>%
  select(Parameter, MAP, Property) %>%
  spread(Parameter, MAP) %>%
  ggplot(., aes( x = b, y = a, size = theta, color = nullB, label = Property))+#, alpha = 1-theta))+
  geom_jitter(width = 2, height = 2, alpha = 0.3)+
  xlim(-3, 65)+
  ylim(-3, 65)
```

Text plot

```{r scatter2_text}
wp.post.summary %>%
  select(Parameter, MAP, Property) %>%
  spread(Parameter, MAP) %>%
  ggplot(., aes( x = b, y = a, size = 1 - theta, color = nullB, label = Property))+#, alpha = 1-theta))+
  geom_text_repel(force = 10, segment.alpha = 0.3)+
  xlim(-3, 65)+
  ylim(-3, 65)
```


NullB only is different when theta is high, which is also when it's less relevant.
(Conclusion: NullB doesn't matter much, could fix it to be 100 for all items)

```{r scatter_nullBvsTheta}
wp.post.summary %>%
  select(Parameter, MAP, Property) %>%
  spread(Parameter, MAP) %>%
  ggplot(., aes( x = theta, y = nullB))+
  geom_point()+
  xlim(0, 1)+
  ylim(0, 100)+
  coord_fixed(ratio = 0.01)
```



##### Mean and variance

```{r scatter1_mean_var}
wp.post.summary %>%
  select(Parameter, MAP, Property) %>%
  spread(Parameter, MAP) %>%
  rowwise() %>%
  mutate(mu = betaMean(a, b),
         sigma = betaSDev(a, b)) %>%
  ggplot(., aes( x = sigma, y = mu, size = theta, color = theta, label = Property))+
  geom_jitter( alpha = 0.3 )
```

Text plot

```{r scatter2_mean_var_text}
wp.post.summary %>%
  select(Parameter, MAP, Property) %>%
  spread(Parameter, MAP) %>%
  rowwise() %>%
  mutate(mu = betaMean(a, b),
         sigma = betaSDev(a, b)) %>%
  ggplot(., aes( x = sigma, y = mu, size = 1 - theta, label = Property))+
  geom_text_repel(force = 10, segment.alpha = 0.3)
```




```{r table1}
wp.post.summary.wide <- wp.post.summary %>%
  select(Parameter, MAP, Property) %>%
  spread(Parameter, MAP)

wp.post.summary.wide[order(-wp.post.summary.wide$a),] %>% kable()
```

#### Within kind prevalence


```{r withinPrevalenceModel}
withinPrevalence <- '
var model = function(){
  var betaParams = betaShape({
    g: uniformDrift({a: 0, b: 1, width: 0.2}),
    d: uniformDrift({a: 0, b: 60, width: 10})
  })

  mapData({data: data}, function(d){
    observe(Beta(betaParams), d.roundedPrevalence)
  })

  return {a: betaParams.a, b: betaParams.b}
}
'
```

```{r runPrevalenceModel}
n_samples = 1000
burn = n_samples

wp.post.within.summary <- data.frame()

for (p in properties){
  categories <- levels(factor(filter(d.tj, Property == p)$Category))
  for (catg in categories){
    
    wp.post <- webppl(program_code = paste(wpHelpers, withinPrevalence, sep = "\n"),
       model_var = "model",
       inference_opts = list(method = "MCMC", samples = n_samples, burn = burn, verbose = TRUE),
       data = d.prev %>% filter(Property == p, Category == catg),
       data_var = "data",
       chains = 3, cores = 3)
  
    wp.post.within.summary <- bind_rows(
      wp.post.within.summary,
      wp.post %>%
        group_by(Parameter) %>%
        summarize(MAP = estimate_mode(value), cred_upper = hdi_upper(value), cred_lower = hdi_lower(value)) %>%
        mutate(Property = p, Category = catg)
    )
    
  print(catg)
  }  
  print(p)
}
save(wp.post.within.summary, file = paste(project.path, model.path, "results/withinPrevParams_mcmc1k_burn1k.Rdata", sep = ""))
```

```{r}
wp.post.within.summary.wide <- left_join(
  wp.post.within.summary %>%
    filter(Parameter == "a") %>%
    rename(a_MAP = MAP, a_cred_upper = cred_upper, a_cred_lower = cred_lower) %>%
    select(-Parameter),
  wp.post.within.summary %>%
    filter(Parameter == "b") %>%
    rename(b_MAP = MAP, b_cred_upper = cred_upper, b_cred_lower = cred_lower) %>%
    select(-Parameter)
)  %>% mutate(maxVal = ifelse(a_MAP > b_MAP, a_MAP, b_MAP))
```
```{r scatter1_prev}
ggplot(wp.post.within.summary.wide, 
       aes( x = b_MAP, y = a_MAP, xmin = b_cred_lower, xmax = b_cred_upper,
            ymin = a_cred_lower, ymax = a_cred_upper))+
  geom_jitter(width = 2, height = 2, alpha = 0.3)+
  xlim(-3, 65)+
  ylim(-3, 65)
```

Text plot

```{r scatter2prev_text}
ggplot(wp.post.within.summary.wide, 
       aes( x = b_MAP, y = a_MAP, xmin = b_cred_lower, xmax = b_cred_upper,
            ymin = a_cred_lower, ymax = a_cred_upper, label = paste(Category, Property)), color = b_MAP)+
  geom_text_repel(force = 4, segment.alpha = 0.3, size = 3) +
  xlim(-30, 63)+
  ylim(-30, 45)
```
```{r scatter2_text_narrowRange}
ggplot(wp.post.within.summary.wide %>% filter(b_MAP < 30, a_MAP< 20), 
       aes( x = b_MAP, y = a_MAP, xmin = b_cred_lower, xmax = b_cred_upper,
            ymin = a_cred_lower, ymax = a_cred_upper, label = paste(Category, Property), color = maxVal))+
  geom_point(size = 0.3)+
  geom_text_repel(force = 4, segment.alpha = 0.3, size = 3)
```
```{r table2}
wp.post.within.summary.wide[order(-wp.post.within.summary.wide$maxVal),] %>% 
  select(Category, Property, a_MAP, b_MAP, a_cred_lower, a_cred_upper, b_cred_lower, b_cred_upper) %>% 
  kable()
```



Examining mean and variance of within-kind prevalence distributions

```{r}
wp.post.within.summary.wide <- wp.post.within.summary.wide %>% 
  rowwise() %>%
   mutate(mu = betaMean(a_MAP, b_MAP),
         sigma = betaSDev(a_MAP, b_MAP))
```


```{r scatter_mu_sigma_prev}
ggplot(wp.post.within.summary.wide, 
       aes( x = mu, y = sigma))+
  geom_point( alpha = 0.3 )
```


Text plot

```{r scatter_mu_sigma_prev_text}
ggplot(wp.post.within.summary.wide, 
       aes( x = sigma, y = mu, label = paste(Category, Property), color = mu))+
  geom_hline(yintercept = 0.5, lty = 3)+
  geom_point(size = 0.8)+
  geom_text_repel(force = 1, segment.alpha = 0.3, size = 3)
```


#### Compare elicited cue validity with prevalence prior derived cue validity

```{r}
cueValidityModel2 <- '

var cueValidity = function(){
  var kind = uniformDraw(data.prior);
  // observe(Bernoulli({p: kind.roundedPrevalence}), true)
  observe(Bernoulli({p: kind.prevalence/100}), true)
  return kind.Category == data.kind[0]
}

expectation(Infer({model: cueValidity}))
'

wp.cueValidity <- data.frame()
for (p in properties){
  categories <- levels(factor(filter(d.tj, Property == p)$Category))
  prevPriorData = d.prev %>% filter(Property == p)
  
  for (catg in categories){

    dataToPass <- list(
      prior = prevPriorData,
      kind = catg
    )
    
    wp.rs <- webppl(cueValidityModel2, 
       packages = c(wp.pkg.path),
       data_var = "data",
       data = dataToPass)
    
    wp.cueValidity <- bind_rows(wp.cueValidity, 
                                data.frame(Category = catg,
                                           Property = p,
                                           cv = wp.rs))
    
  }
  print(p)
}

```



Empirical cue validity

```{r}
d.cv.summary <- d.cv.out %>% 
  group_by(Category, Property) %>%
  multi_boot_standard(column = "response")
```

```{r}
left_join(d.cv.summary, wp.cueValidity) %>%
  ggplot(., aes( x = cv, y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_abline(intercept = 0, slope = 1, lty = 3, alpha = 0.3)+
  geom_point()+
  geom_errorbar(alpha = 0.3) +
  xlim(0, 1) + ylim(0, 1) + 
  coord_fixed() + 
  xlab("Prevalence prior derived CV")+
  ylab("Empirical CV")
  

with(left_join(d.cv.summary, wp.cueValidity), 
     cor(cv, mean, use = "pairwise.complete.obs"))

#ggsave("~/Desktop/cueValidity-empirical-vs-prevPriorderived_raw.pdf",
       #width = 4, height = 4)
```




### Regression model

```{r}
regressionModel <- '
var withItParams = data.prior[0], nullParams = {a:1 , b: 100}

var totalNKinds = 30;
var mainCProb = data.prior[0]["theta"];
var kindsWithIt = mainCProb * totalNKinds

var prev = utils.closest(midBins, data.prev[0]["mu"]);

// this is assuming k is within mainComponent
var cueValidity = function(){
  var mainComponent = flip(mainCProb);
  var prevalencePrior = DiscretizedBeta( mainComponent ? withItParams : nullParams )
  observe(prevalencePrior, prev)
  var pfk = sample(prevalencePrior)
  var f = flip(pfk);
  condition(f);
  return mainComponent
}

var b  = {
  cv: 8, prev: 2
}

var cueValidity = Math.exp(Infer({model: cueValidity}).score(true)) / kindsWithIt;
display(cueValidity)
display(prev)
var cvSpeaker = Infer({model: function(){
  var generic = flip(Math.exp(-4)); // "generic" ?
  factor( generic ? (b.cv*cueValidity + b.prev*prev) : 0)
  return generic
}})

expectation(cvSpeaker)
'
```

```{r}
for (p in properties){
  categories <- levels(factor(filter(d.tj, Property == p)$Category))
  priorParams <- wp.post.summary.wide %>% filter(Property == p)
  
  for (catg in categories){
    prevParams <- wp.post.within.summary.wide %>% filter(Property == p, Category == catg)

    dataToPass <- list(
      prior = priorParams,
      prev = prevParams
    )
    
    webppl(regressionModel, 
           packages = c(wp.pkg.path),
           data_var = "data",
           data = dataToPass)
    
  }
}
```





