---
title: "Interpretations of novel generics"
author: "mht"
date: "August 12, 2015"
output: html_document
---


```{r}
library(tidyr)
library(dplyr)
library(langcog)
library(Metrics)


histToSamples <- function(df, samples){
  rows <- rep.int(seq_len(nrow(df)), times = round(df$Probability * samples))
  cols <- names(df) != "Probability"
  df[rows, cols, drop = FALSE]
}


setwd("~/Documents/research/generics-paper/")
df <- read.csv("data/unfamiliar_generics/interpretations-trials.csv")
```


# Implied prevalence by item

```{r}
d.impItem <- df %>%
  group_by(stim_property, stim_type) %>%
  multi_boot_standard(column = "response")

d.impItem$stim_property<-with(d.impItem, 
                         reorder(stim_property, mean, function(x) x))

ggplot(data=d.impItem, aes(x=stim_property, y=mean, fill= stim_type))+
  geom_bar(stat='identity',position=position_dodge(), alpha=0.8)+
  geom_errorbar(aes(ymin=ci_lower,ymax=ci_upper), width=0.5,
                color='black')+
  xlab("")+
  ylab("\n implied prevalence")+
  coord_flip()
```


# L1 Model predictions

Load model results


```{r}
m.samp <- data.frame()

for (i in 1:3) { 
  mi <- as.data.frame(fread(paste("~/Documents/research/generics/manuscript/model-results/novel_generics/novel-interpretations-so1-integrateTheta_IncrMH100000_burn50000_c",i,".csv", sep="")))
  m.samp <- bind_rows(m.samp, histToSamples(mi, 100000))
}
```

Posterior over s1 parameter

```{r}

m.samp %>% 
  filter(Parameter == "s1_optimality") %>%
  ggplot(., aes(x = Value))+
  theme_paper()+
  geom_histogram(aes(y=..count../sum(..count..)), binwidth = 0.75)+
  facet_wrap(~Parameter, scales='free')+
  xlim(0,20)+
  ylab("Posterior probability")


ggsave(file="~/Documents/research/generics/manuscript/figures/unfamiliar-interpretations-parameter.pdf", width = 5, height =4)


m.samp %>% 
  filter(Parameter == "s1_optimality") %>% 
  group_by(Parameter) %>%
  summarise(postMode = estimate_mode(Value),
            credHi = hdi_upper(Value),
            credLo = hdi_lower(Value))
```


Posterior predictive

```{r}
m.pred <- m.samp %>% 
  filter(Parameter == "implied_prevalence") %>%
  group_by(Property) %>%
  summarise(postMode = estimate_mode(Value),
            credHi = hdi_upper(Value),
            credLo = hdi_lower(Value))

df.md <- left_join(
  d.impItem %>%
    rename(Property = stim_property),
  m.pred)

ggplot(df.md, aes(x = postMode, xmin = credLo, xmax = credHi,
                  y = mean, ymin = ci_lower, ymax = ci_upper, color = stim_type))+
  geom_abline(intercept = 0, slope = 1, lty = 2)+
  theme_paper()+
  geom_errorbar()+
  geom_errorbarh()+
  geom_point() +
  xlim(0.25,1.01)+
  ylim(0.25,1.01)+
  coord_fixed()

with(df.md, cor(postMode, mean))^2
with(df.md, mse(mean, postMode))
```


# Add legend to correspond to Expt. 2c

### Simple analyze prior data by item

By item, prevalence implied by observing one instance with the property (mean prevalence when present)

```{r}
df.prior <- read.csv("data/unfamiliar_generics/unfamiliar-priors.csv")

d.priorItem <- df.prior %>%
  group_by(stim_property, stim_type) %>%
  multi_boot_standard(column = "prevWithin")

d.priorItem$stim_property<-with(d.priorItem, 
                         reorder(stim_property, mean, function(x) x))

ggplot(data=d.priorItem, aes(x=stim_property, y=mean, fill= stim_type))+
  geom_bar(stat='identity',position=position_dodge(), alpha=0.8)+
  geom_errorbar(aes(ymin=ci_lower,ymax=ci_upper), width=0.5,
                color='black')+
  xlab("")+
  ylab("\n implied prevalence")+
  coord_flip()
```

Split accidental/disease by median of the prior data

```{r}
accidental.prior.median <- d.priorItem %>%
  filter(stim_type == "accidental/disease") %>%
  ungroup() %>%
  group_by(stim_type) %>%
  summarize(med = median(mean))

d.priorItem <- bind_rows(
  d.priorItem %>% 
    filter(stim_type != "accidental/disease"),
  d.priorItem %>%
    filter(stim_type == "accidental/disease") %>%
    mutate(stim_type = ifelse(mean > accidental.prior.median$med,
                              "commonAccidental",
                              "rareAccidental"))
)

ggplot(data=d.priorItem, aes(x=stim_property, y=mean, fill= stim_type))+
  geom_bar(stat='identity',position=position_dodge(), alpha=0.8)+
  geom_errorbar(aes(ymin=ci_lower,ymax=ci_upper), width=0.5,
                color='black')+
  xlab("")+
  ylab("\n implied prevalence")+
  coord_flip()
```


Merge median split labels with df.md, which holds model predictions and human data

```{r}


df.md.split <- left_join(df.md %>% dplyr::select(-stim_type),
                         d.priorItem %>% dplyr::select(stim_property, stim_type) %>% 
                           rename(Property = stim_property)) %>%
  ungroup() %>%
  mutate(Property = factor(stim_type, levels = c("bodyParts",
                                                 "vagueParts",
                                                 "colorParts",
                                                 "commonAccidental",
                                                 "rareAccidental"),
                           labels = c("body parts",
                                                 "vague parts",
                                                 "color parts",
                                                 "common accidental",
                                                 "rare accidental")))

ggplot(df.md.split, aes(x = postMode, xmin = credLo, xmax = credHi,
                  y = mean, ymin = ci_lower, ymax = ci_upper, color = Property))+
  geom_abline(intercept = 0, slope = 1, lty = 2)+
  theme_paper()+
  geom_errorbar(alpha = 0.7)+
  geom_errorbarh(alpha = 0.7)+
  geom_point(size = 3) +
  xlim(0.25,1.01)+
  ylim(0.25,1.01)+
  coord_fixed()+
  scale_color_brewer(palette="Set1")+
  xlab("Model posterior predictive")+
  ylab("Human interpretation of prevalence")+
  guides(color = FALSE)


ggsave(file="~/Documents/research/generics/manuscript/figures/unfamiliar-interpretations-model-data.pdf", width = 6, height =5)


```


### Does a priori mean prevalence when present (Gamma) predict implied prevalence?


```{r prior.prevalence.byItem}
d1<-read.csv("~/Documents/research/generics/manuscript/model-results/generics-asym-priorByItem-incrmh100000_burn50000a.csv")
d2<-read.csv("~/Documents/research/generics/manuscript/model-results/generics-asym-priorByItem-incrmh100000_burn50000b.csv")
d3<-read.csv("~/Documents/research/generics/manuscript/model-results/generics-asym-priorByItem-incrmh100000_burn50000c.csv")

samples = 50000
d.tidy<-bind_rows(d1,d2,d3)


#d.tidy <- d


d.params<-data.frame(Parameter = rep(d.tidy$Parameter, 
                               1+samples*d.tidy$Probability),
                     Item = rep(d.tidy$Item, 
                               1+samples*d.tidy$Probability),
                Prevalence = rep(d.tidy$Prevalence, 
                               1+samples*d.tidy$Probability),
                Response = rep(d.tidy$Value, 
                               1+samples*d.tidy$Probability))
  


d.summary<-d.params %>% 
  group_by(Parameter,Item, Prevalence) %>%
  summarise(expectation = mean(Response),
              MAP = estimate_mode(Response),
            credHi = HPDhi(Response),
            credLo = HPDlo(Response))



d.impWPrev<-left_join(d.implied,
          d.summary %>% filter(Item=='response1' & Prevalence=='gamma') %>%
            select(Parameter, MAP) %>%
            rename(stim_property=Parameter))


rs<-lmer(data=d.impWPrev,
     response~MAP+ (1+MAP|workerid))
summary(rs)

 
d.mcp<-d.summary %>% filter(Item=='response1' & Prevalence =='gamma') %>%
  rename(priorMAP = MAP, 
         priorHigh = credHi,
         priorLow = credLo) %>%
  ungroup() %>%
  select(-Item, -Prevalence) %>%
  rename(Item = Parameter)

dmp.items<-left_join(dm.items, d.mcp)

with(dmp.items, cor(priorMAP, response))^2
with(dmp.items, mse(priorMAP, response))

ggplot(dmp.items, aes(x=priorMAP, y = response, color = type))+
  geom_point()+
  geom_abline(intercept = 0, slope = 1, linetype=2)+
  geom_errorbar(aes(ymin = YMin, ymax=YMax))+
  geom_errorbarh(aes(xmin = priorLow, xmax = priorMAP))+
  xlim(0,1)+
  ylim(0,1)+
  xlab("Mean conditional prevalence")+
  ylab("Human judgment")+
  scale_color_brewer(palette='Set1')+
  coord_fixed()+
  guides(color=guide_legend(title="Property type"))

#ggsave(file='~/Documents/research/generics/manuscript/figures/implied-mcp-byItem-mh100kX2.pdf')

```







Linear regression: Implied prevalence vs. A priori Within-prevalence
```{r}

d.reg<-left_join(d.implied, d.within %>% rename(type=Parameter))

rs<-lmer(response ~ MAPwithin + (1 + MAPwithin | workerid), d.reg)
summary(rs)
```
Linear regression: Implied prevalence > A priori Within-prevalence

```{r}
d.reg1<-d.reg %>%
  select(MAPwithin, response, stim_property, workerid)  %>%
  gather(key, val, -stim_property, -workerid)

rs1<-lmer(val ~  key + (1 | workerid) + (1 + key | stim_property), data=d.reg1)  

summary(rs1)

priorSD<-d.reg1 %>% filter(key=="MAPwithin") %>% summarise(sd(val))
posteriorSD<-d.reg1 %>% filter(key=="response") %>% summarise(sd(val))
pooled.sd <- sqrt((39*(priorSD^2) + 39*(posteriorSD^2))/78)

cohen.d <- 0.1725 / pooled.sd

```


```{r}
dmp.test<-dmp.items %>%
  select(Item, response, priorMAP)

summary(rs1)

```

```{r}


d.aveAccPrev <- d.accept %>%
  mutate(response = as.numeric(response==1)) %>%
  group_by(workerid, type) %>%
  summarise(prev = avePrevScore(response,stim_prevalence)) %>%
  mutate(src = "accept") 

d.reg.tc<-left_join(d.aveAccPrev, d.within %>% rename(type=Parameter))



rs.tc<-lmer(prev ~ MAPwithin+ (1 + MAPwithin | workerid), d.reg.tc)

summary(rs.tc)



d.reg.tc$workerid<- max(to.n(levels(factor(d.reg$workerid)))) + d.reg.tc$workerid

d.reg <- d.reg %>% select(workerid, type, response, MAPwithin, credHiWithin, credLoWithin) %>%
  rename(prev = response) %>%
  mutate(src = 'implied')

d.reg.joint<- bind_rows(d.reg, d.reg.tc)

rs.tc<-lmer(prev ~ MAPwithin*src - src + (1 + MAPwithin | workerid), d.reg.joint)

summary(rs.tc)
```
