---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(forcats)
library(langcog)
library(knitr)
project.path <- "~/Documents/research/generics-paper/"
```


### Subject information

```{r}
df.subj <- read.csv(paste(project.path, "data/habituals/priors/friends-and-family-1-subject_information.csv", sep= ""))
```

Did people like the HIT?
```{r}
table(df.subj$enjoyment)
```

Where are people from?

```{r}
table(df.subj$country_name)
```

### Results

```{r}
df <- read.csv(paste(project.path, "data/habituals/priors/friends-and-family-1-trials.csv", sep= ""))
```

How participants filled out each item? (Each participant did 15 items, randomly selected from 27)
```{r}
tab.items <- table(unique(
  df %>% 
    select(workerid, action)
)$action)

df.items <- data.frame(tab.items)

df.items[order(df.items$Freq),] %>% kable()
```


How often do you fill out all 0s?

```{r}
df.allZeros <- df %>%
  filter(person != "hypothetical") %>%
  group_by(workerid, action) %>%
  summarize(counts = sum(n_times)) %>%
  mutate(zeros = ifelse(counts == 0, 1, 0)) %>% 
  ungroup() %>%
  group_by(action) %>%
  summarize(n = n(),
            allZeros = sum(zeros)) %>%
  ungroup() %>%
  mutate(action = factor(action, levels = action[order(allZeros)]),
         knowSomebody = n - allZeros) 

ggplot(df.allZeros %>% gather(key, val, knowSomebody, allZeros), 
       aes(x = action, y = val, fill = key))+
  geom_bar(stat = 'identity')+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_solarized()+
  coord_flip()
```
When you fill out "all 0s", do you go for the hypothetical?

```{r allZeros}
df.hypotheticals <- 
  left_join(
    df %>%
      filter(person != "hypothetical") %>%
      group_by(workerid, action) %>%
      summarize(counts = sum(n_times)) %>%
      filter(counts == 0) %>%
      ungroup(),
    df %>%
      filter(person == "hypothetical") %>%
      select(workerid, action, person)
  ) %>%
  mutate(hypothetical = ifelse(is.na(person), 0, 1)) %>%
  group_by(action) %>%
  summarize(nZeros = n(),
            nHypotheticals = sum(hypothetical)) %>%
  mutate(action = factor(action, levels = action[order(nZeros)]),
         noHypothetical = nZeros - nHypotheticals) %>%
  gather(key, val, noHypothetical, nHypotheticals)

ggplot(df.hypotheticals, aes(x = action, y = val, fill = key)) +
  geom_bar(stat = 'identity', color = 'black') +
  theme(axis.text.x = element_text(angle = 90)) +
  coord_flip() +
  scale_fill_solarized()
```


What time window do people select?

```{r timeWindow}
df %>%
  mutate(interval = fct_relevel(interval, "5 years", "year", "month", "week")) %>%
  ggplot(., aes ( x = interval, fill = interval ))+
  geom_bar()+
  facet_wrap(~action)+
  scale_fill_solarized()+
  theme(axis.text.x = element_blank())
```



Put rates on the scale of Number of times / year

```{r}
annualRates = list("5 years" = 1/5, "year" = 1, "month" = 12, "week" = 52)

df.tidy <- df %>%
  rowwise() %>%
  mutate(annualRate = annualRates[[as.character(interval)]]*n_times)

df.tidy %>%
  filter(annualRate > 0 ) %>%
  ggplot(., aes( x = log(annualRate)))+
  #geom_histogram()+
  geom_density()+
  facet_wrap(~action, scales = 'free')+
  xlim(-2, 8.5)

ggsave("~/Desktop/habpriors_ff.pdf", width = 12, height = 8)
```


```{r}

df.tidy %>%
  mutate(annualRate = ifelse(annualRate == 0, 0.05, annualRate)) %>%
  ggplot(., aes( x = log(annualRate)))+
  geom_histogram()+
  #geom_density()+
  facet_wrap(~action, scales = 'free')+
  xlim(-3.5, 8.5)

#ggsave("~/Desktop/habpriors_ff_wZeros_Hist.pdf", width = 12, height = 8)
```

# Comparison with structured elicitation

### Mixture parameter vs. No. 0s

```{r}
df.s.e <- read.csv(paste(project.path, 
                       "models/habituals/data/prior2-existence.csv", 
                       sep = ""))

df.s.e.summ <- df.s.e %>%
  group_by(item) %>%
  multi_boot_standard(column = "val")
```

```{r}
 df.e.summ <- df %>%
  mutate(existence = ifelse(n_times > 0, 1, 0)) %>%
  group_by(action) %>%
  multi_boot_standard(column = "existence") %>%
  rename(friends_mean = mean,
         friends_lower = ci_lower,
         friends_upper = ci_upper)

df.mixture <- left_join(df.s.e.summ %>% rename(action = item), 
                        df.e.summ %>%
                          mutate(action = as.character(action),
                                 action = 
                                   ifelse(action == "sell things on eBay",
                                          "sells things on eBay",
                                          action)))

df.mixture[complete.cases(df.mixture), ] %>%
  ggplot(., aes ( x = friends_mean, xmin = friends_lower,
                  xmax = friends_upper,
                  y = mean, ymin = ci_lower,
                  ymax = ci_upper))+
  geom_point()+
  geom_errorbar(alpha = 0.4)+
  geom_errorbarh(alpha = 0.4)+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  xlim(0, 1)+
  ylim(0, 1)+
  coord_fixed()+
  xlab("# of friends who have do X w/ non-0 freq")+
  ylab("proportion of Americans who have done X before")

ggsave("~/Desktop/habpriors_comparison_scatter_HasDoneIt.pdf", width = 5, 
       height = 6)
```

```{r}
df.mixture.complete <- df.mixture[complete.cases(df.mixture), ] %>%
  mutate(sqErr = (mean - friends_mean) ^2 )

df.mixture.complete[order(-df.mixture.complete$sqErr), ] %>%
  select(action, friends_mean, mean, sqErr) %>%
  kable()

df.mixture.complete[order(-df.mixture.complete$sqErr), ] %>%
  head(8) %>%
  select(action, friends_mean, mean, sqErr) %>%
  kable(format = "markdown")
```


```{r}
df.s.f <- read.csv(paste(project.path, 
                       "models/habituals/data/prior2-timesper5yr.csv", 
                       sep = ""))
df.f <- bind_rows(df.s.f %>%
            mutate(val = val/5,
                   logval = log(val),
                   src = 'american') %>%
            rename(action = item) %>%
              select(action, logval, src),
          df %>%
            filter(n_times > 0) %>%
            rowwise() %>%
          mutate(friendRate =
                   annualRates[[as.character(interval)]]*n_times,
                 logval = log(friendRate),
                 src = 'friends') %>%
            select(action, logval, src))

ggplot(df.f %>%
         filter(!(action %in% c("smokes marijuana", "does cocaine",
                              "steals cars", "steals chewing gum"))) %>%
         mutate(action = as.character(action),
                 action = 
                   ifelse(action == "sell things on eBay",
                          "sells things on eBay",
                                          action)), 
       aes( x = logval, lty = src, color = src))+
  stat_ecdf()+
  facet_wrap(~action)+
  scale_color_solarized()+
  scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
  theme(strip.text.y = element_text(angle = 0))

ggsave("~/Desktop/habpriors_comparison_cdfs_DoesIt.pdf", width = 10, 
       height = 8)

```

