---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(forcats)
library(langcog)
library(knitr)
project.path <- "~/Documents/research/generics-paper/"
```


### Subject information

```{r}
df.subj <- read.csv(paste(project.path, "data/habituals/priors/friends-and-family-1-subject_information.csv", sep= ""))
```

Did people like the HIT?
```{r}
table(df.subj$enjoyment)
```

Where are people from?

```{r}
table(df.subj$country_name)
```

### Results

```{r}
df <- read.csv(paste(project.path, "data/habituals/priors/friends-and-family-1-trials.csv", sep= ""))
```

How participants filled out each item? (Each participant did 15 items, randomly selected from 27)
```{r}
tab.items <- table(unique(
  df %>% 
    select(workerid, action)
)$action)

df.items <- data.frame(tab.items)

df.items[order(df.items$Freq),] %>% kable()
```


How often do you fill out all 0s?

```{r}
df.allZeros <- df %>%
  filter(person != "hypothetical") %>%
  group_by(workerid, action) %>%
  summarize(counts = sum(n_times)) %>%
  mutate(zeros = ifelse(counts == 0, 1, 0)) %>% 
  ungroup() %>%
  group_by(action) %>%
  summarize(n = n(),
            allZeros = sum(zeros)) %>%
  ungroup() %>%
  mutate(action = factor(action, levels = action[order(allZeros)]),
         knowSomebody = n - allZeros) 

ggplot(df.allZeros %>% gather(key, val, knowSomebody, allZeros), 
       aes(x = action, y = val, fill = key))+
  geom_bar(stat = 'identity')+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_solarized()+
  coord_flip()
```
When you fill out "all 0s", do you go for the hypothetical?

```{r allZeros}
df.hypotheticals <- 
  left_join(
    df %>%
      filter(person != "hypothetical") %>%
      group_by(workerid, action) %>%
      summarize(counts = sum(n_times)) %>%
      filter(counts == 0) %>%
      ungroup(),
    df %>%
      filter(person == "hypothetical") %>%
      select(workerid, action, person)
  ) %>%
  mutate(hypothetical = ifelse(is.na(person), 0, 1)) %>%
  group_by(action) %>%
  summarize(nZeros = n(),
            nHypotheticals = sum(hypothetical)) %>%
  mutate(action = factor(action, levels = action[order(nZeros)]),
         noHypothetical = nZeros - nHypotheticals) %>%
  gather(key, val, noHypothetical, nHypotheticals)

ggplot(df.hypotheticals, aes(x = action, y = val, fill = key)) +
  geom_bar(stat = 'identity', color = 'black') +
  theme(axis.text.x = element_text(angle = 90)) +
  coord_flip() +
  scale_fill_solarized()
```


What time window do people select?

```{r timeWindow}
df %>%
  mutate(interval = fct_relevel(interval, "5 years", "year", "month", "week")) %>%
  ggplot(., aes ( x = interval, fill = interval ))+
  geom_bar()+
  facet_wrap(~action)+
  scale_fill_solarized()+
  theme(axis.text.x = element_blank())
```



Put rates on the scale of Number of times / year

```{r}
annualRates = list("5 years" = 1/5, "year" = 1, "month" = 12, "week" = 52)

df.tidy <- df %>%
  rowwise() %>%
  mutate(annualRate = annualRates[[as.character(interval)]]*n_times)

df.tidy %>%
  filter(annualRate > 0 ) %>%
  ggplot(., aes( x = log(annualRate)))+
  #geom_histogram()+
  geom_density()+
  facet_wrap(~action, scales = 'free')+
  xlim(-2, 8.5)
# 
# ggsave("~/Desktop/habpriors_ff.pdf", width = 12, height = 8)
```


```{r}

df.tidy %>%
  mutate(annualRate = ifelse(annualRate == 0, 0.05, annualRate)) %>%
  ggplot(., aes( x = log(annualRate)))+
  geom_histogram()+
  #geom_density()+
  facet_wrap(~action, scales = 'free')+
  xlim(-3.5, 8.5)

#ggsave("~/Desktop/habpriors_ff_wZeros_Hist.pdf", width = 12, height = 8)
```

Output for model

```{r fig.height = 14, fig.width = 12}
df.out <- df.tidy %>%
  mutate(annualRate = ifelse(annualRate == 0, 0.15, annualRate),
         lograte = log(annualRate),
         binned_lograte = round(lograte*2)/2) %>%
  group_by(action, binned_lograte) %>%
  summarize(counts = n())


# make sure 0s are represented
df.out2 <- left_join(
  expand.grid(action = levels(df.out$action), binned_lograte = levels(factor(df.out$binned_lograte))),
  df.out %>% mutate(binned_lograte = factor(binned_lograte))) 

df.out2[is.na(df.out2)] <- 0
df.out2 <- df.out2 %>%
  mutate(binned_lograte = as.numeric(binned_lograte))
  
ggplot(df.out2, aes( x = binned_lograte, y = counts))+
  #geom_histogram()+
  geom_bar(stat = 'identity', position = position_dodge())+
  #geom_density()+
  facet_wrap(~action, scales = 'free')+
  xlim(-3.5, 8.5)

write.csv(df.out2 %>%
  spread(binned_lograte, counts) %>%
  mutate(action = as.character(action),
         action = ifelse(action == "sell things on eBay",
                                          "sells things on eBay",
                                          action)), "~/Documents/research/generics-paper/models/habituals/data/ff-prior-n50.csv", row.names = F)

```
```{r}
df.tidy %>%
  mutate(annualRate = ifelse(annualRate == 0, 0.15, annualRate),
         lograte = log(annualRate),
         binned_lograte = round(lograte*2)/2) %>%
  group_by(binned_lograte) %>%
  summarize(counts = n()) %>% View()

```


# Comparison with structured elicitation

### Mixture parameter vs. No. 0s

```{r}
df.s.e <- read.csv(paste(project.path, 
                       "models/habituals/data/prior2-existence.csv", 
                       sep = ""))

df.s.e.summ <- df.s.e %>%
  group_by(item) %>%
  multi_boot_standard(column = "val")
```

```{r}
 df.e.summ <- df %>%
  mutate(existence = ifelse(n_times > 0, 1, 0)) %>%
  group_by(action) %>%
  multi_boot_standard(column = "existence") %>%
  rename(friends_mean = mean,
         friends_lower = ci_lower,
         friends_upper = ci_upper)

df.mixture <- left_join(df.s.e.summ %>% rename(action = item), 
                        df.e.summ %>%
                          mutate(action = as.character(action),
                                 action = 
                                   ifelse(action == "sell things on eBay",
                                          "sells things on eBay",
                                          action)))

df.mixture[complete.cases(df.mixture), ] %>%
  ggplot(., aes ( x = friends_mean, xmin = friends_lower,
                  xmax = friends_upper,
                  y = mean, ymin = ci_lower,
                  ymax = ci_upper))+
  geom_point()+
  geom_errorbar(alpha = 0.4)+
  geom_errorbarh(alpha = 0.4)+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  xlim(0, 1)+
  ylim(0, 1)+
  coord_fixed()+
  xlab("# of friends who have do X w/ non-0 freq")+
  ylab("proportion of Americans who have done X before")

ggsave("~/Desktop/habpriors_comparison_scatter_HasDoneIt.pdf", width = 5, 
       height = 6)
```

```{r}
df.mixture.complete <- df.mixture[complete.cases(df.mixture), ] %>%
  mutate(sqErr = (mean - friends_mean) ^2 )

df.mixture.complete[order(-df.mixture.complete$sqErr), ] %>%
  select(action, friends_mean, mean, sqErr) %>%
  kable()

df.mixture.complete[order(-df.mixture.complete$sqErr), ] %>%
  head(8) %>%
  select(action, friends_mean, mean, sqErr) %>%
  kable(format = "markdown")
```


```{r}
df.s.f <- read.csv(paste(project.path, 
                       "models/habituals/data/prior2-timesper5yr.csv", 
                       sep = ""))
df.f <- bind_rows(df.s.f %>%
            mutate(val = val/5,
                   logval = log(val),
                   src = 'american') %>%
            rename(action = item) %>%
              select(action, logval, src),
          df %>%
            filter(n_times > 0) %>%
            rowwise() %>%
          mutate(friendRate =
                   annualRates[[as.character(interval)]]*n_times,
                 logval = log(friendRate),
                 src = 'friends') %>%
            select(action, logval, src))

ggplot(df.f %>%
         filter(!(action %in% c("smokes marijuana", "does cocaine",
                              "steals cars", "steals chewing gum"))) %>%
         mutate(action = as.character(action),
                 action = 
                   ifelse(action == "sell things on eBay",
                          "sells things on eBay",
                                          action)), 
       aes( x = logval, lty = src, color = src))+
  stat_ecdf()+
  facet_wrap(~action)+
  scale_color_solarized()+
  scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
  theme(strip.text.y = element_text(angle = 0))

ggsave("~/Desktop/habpriors_comparison_cdfs_DoesIt.pdf", width = 10, 
       height = 8)

```


## Baseline models from prior

```{r}
df.baseline <- left_join(df.tidy %>%
  rowwise() %>%
  mutate(isZero = ifelse(n_times == 0 , 1, 0)) %>%
  group_by(action) %>%
  summarise(nZeros = sum(isZero),
            n = n()),
  df.tidy %>%
    filter(n_times > 0) %>%
    group_by(action) %>%
    summarise(aveFreq = mean(annualRate))
) %>%
  mutate(rarity = nZeros / n,
         logFreq = log(aveFreq))
```

```{r}
df.baseline <- df.tidy %>%
    group_by(action) %>%
    summarise(aveFreq = mean(annualRate)) %>%
  mutate(logAveFreq = log(aveFreq))
```

```{r}
d.hab <- read.csv(paste(project.path, data.path, "tj-2-logtimes.csv", sep = ""))


annualRates = list("5 years" = 1/5, 
                   "2 years" = 1/2,
                   "year" = 1, 
                   "6 months" = 2,
                   "2 months" = 6,
                   "month" = 12, 
                   "2 weeks" = 26,
                   "week" = 52)

df.hab.tidy <- d.hab %>%
  rowwise() %>%
  mutate(annualRate = annualRates[[as.character(time_period)]]*n_instances,
         logTargetRate =log(annualRate), 
         response = ifelse(response == "agree-key", 1, 0)) %>%
  select(workerid, habitual, logTargetRate, response, time_period)

df.hab.baseline <- left_join(
  df.baseline %>% rename(habitual = action) %>%
    mutate(habitual = as.character(habitual),
           habitual = ifelse(habitual == "sell things on eBay",
                                          "sells things on eBay",
                                          habitual)), 
  df.hab.tidy)


%>%
  mutate(propFreq = log(exp(logTargetRate)/exp(logFreq)) )
 

glm.res <- glm(response ~ logAveFreq + logTargetRate, data = df.hab.baseline, family = 'binomial')

glm.model.predictions <- unique(
  select(df.hab.baseline, -aveFreq, -workerid, -response)
#  select(df.hab.baseline,-nZeros, -n, -aveFreq, -workerid, -response)
  )

glm.model.predictions <- glm.model.predictions %>%
  mutate(prediction = predict(glm.res, ., type = "response"))


d.hab.summary <- df.hab.tidy %>% 
  mutate(response = ifelse(response == "agree-key", 1, 0)) %>%
  group_by(habitual, time_period, annualRate) %>%
  multi_boot_standard(column = "response")

df.hab.summary.baseline <- left_join(
  df.baseline %>% rename(habitual = action) %>%
    mutate(habitual = as.character(habitual),
           habitual = ifelse(habitual == "sell things on eBay",
                                          "sells things on eBay",
                                          habitual)), 
  d.hab.summary) %>%
  mutate(targetLogRate = log(annualRate))

df.hab.summary.baseline.lmPreds <- left_join(df.hab.summary.baseline, glm.model.predictions %>% rename(targetLogRate = logTargetRate))

```


```{r fig.width = 7}
ggplot(df.hab.summary.baseline.lmPreds, aes (x = prediction, y = mean, ymin = ci_lower, ymax = ci_upper))+
  geom_errorbar(alpha = 0.3)+
  geom_abline(intercept = 0, slope = 1, lty = 3)+
  # geom_text_repel(data = d.tj.w.glm %>% rename(cuevalidity = prop) %>% 
  #                   filter(prediction > 0.14, prediction < 0.9), 
  #                 aes(label = item, color = cuevalidity), force = 1, size = 3)+
  geom_point()+
  xlim(0,1)+
  ylim(0,1)+
  coord_fixed()+
  xlab("Logistic model prediction")+
  ylab("Human habitual endorsement")
```


$$r^2_{pearson}(`r length(df.hab.summary.baseline.lmPreds$habitual)`) = `r with(df.hab.summary.baseline.lmPreds, cor(mean, prediction, use = "pairwise.complete.obs"))^2`$$

$$r_{spearman}(`r length(df.hab.summary.baseline.lmPreds$habitual)`) = `r with(df.hab.summary.baseline.lmPreds, cor(mean, prediction, use = "pairwise.complete.obs", method = "spearman"))`$$

```{r}
df.hab.summary.baseline.lmPreds <- df.hab.summary.baseline.lmPreds %>% mutate(sqErr = (mean - prediction) ^ 2)

df.hab.summary.baseline.lmPreds[with(df.hab.summary.baseline.lmPreds, order(-sqErr)), ] %>% ungroup() %>%
  select(habitual, time_period, mean, prediction, logAveFreq, targetLogRate, sqErr) %>%
  rename(humanEndorse = mean) %>% kable()
```


