---
title: "Friends and family 2"
output: html_notebook
---

```{r}
library(tidyverse)
library(forcats)
library(langcog)
library(knitr)
project.path <- "~/Documents/research/communicating-generalizations/"
```

Ran 4/18/2017

### Subject information

```{r}
df.subj <- read.csv(paste(project.path, "data/habituals/priors/friends-and-family-2-subject_information.csv", sep= ""))
```

Did people like the HIT?
```{r}
table(df.subj$enjoyment)
```

Where are people from?

```{r}
table(df.subj$country_name)
```

### Results

```{r}
df <- read.csv(paste(project.path, "data/habituals/priors/friends-and-family-2-trials.csv", sep= ""))
```

How participants filled out each item? (Each participant did 15 items, randomly selected from 27)
```{r}
tab.items <- table(unique(
  df %>% 
    select(workerid, action)
)$action)

df.items <- data.frame(tab.items)

df.items[order(df.items$Freq),] %>% kable()
```


How often do you fill out all 0s?

```{r}
df.allZeros <- df %>%
  filter(person != "hypothetical") %>%
  group_by(workerid, action) %>%
  summarize(counts = sum(n_times)) %>%
  mutate(zeros = ifelse(counts == 0, 1, 0)) %>% 
  ungroup() %>%
  group_by(action) %>%
  summarize(n = n(),
            allZeros = sum(zeros)) %>%
  ungroup() %>%
  mutate(action = factor(action, levels = action[order(allZeros)]),
         knowSomebody = n - allZeros) 

ggplot(df.allZeros %>% gather(key, val, knowSomebody, allZeros), 
       aes(x = action, y = val, fill = key))+
  geom_bar(stat = 'identity')+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_solarized()+
  coord_flip()
```
When you fill out "all 0s", do you go for the hypothetical?

```{r allZeros}
df.hypotheticals <- 
  left_join(
    df %>%
      filter(person != "hypothetical") %>%
      group_by(workerid, action) %>%
      summarize(counts = sum(n_times)) %>%
      filter(counts == 0) %>%
      ungroup(),
    df %>%
      filter(person == "hypothetical") %>%
      select(workerid, action, person)
  ) %>%
  mutate(hypothetical = ifelse(is.na(person), 0, 1)) %>%
  group_by(action) %>%
  summarize(nZeros = n(),
            nHypotheticals = sum(hypothetical)) %>%
  mutate(action = factor(action, levels = action[order(nZeros)]),
         noHypothetical = nZeros - nHypotheticals) %>%
  gather(key, val, noHypothetical, nHypotheticals)

ggplot(df.hypotheticals, aes(x = action, y = val, fill = key)) +
  geom_bar(stat = 'identity', color = 'black') +
  theme(axis.text.x = element_text(angle = 90)) +
  coord_flip() +
  scale_fill_solarized()
```


What time window do people select?

```{r timeWindow, fig.width = 6, fig.height = 4}
df %>%
  mutate(interval = fct_relevel(interval, "5 years", "2 years", "year", "6 months","2 months","month", "2 weeks", "week")) %>%
  ggplot(., aes ( x = interval, fill = interval ))+
  geom_bar()+
  facet_wrap(~action)+
  scale_fill_solarized()+
  theme(axis.text.x = element_blank())
```



Put rates on the scale of Number of times / year

```{r fig.height = 4, fig.width = 6}
annualRates = list("5 years" = 1/5, "2 years" = 1/2,
                   "year" = 1, "6 months" = 2, "2 months" = 6,
                   "month" = 12, "2 weeks" = 26 ,"week" = 52)

df.tidy <- df %>%
  rowwise() %>%
  mutate(annualRate = annualRates[[as.character(interval)]]*n_times)


df.tidy %>%
  filter(annualRate > 0) %>%
  #mutate(annualRate = ifelse(annualRate == 0, 0.05, annualRate)) %>%
  #ggplot(., aes( x = log(annualRate)))+
  ggplot(., aes( x = annualRate))+
  geom_histogram()+
  #geom_density()+
  facet_wrap(~action, scales = 'free')+
  xlab("N times per year")


```



```{r fig.height = 4, fig.width = 6}
df.tidy %>%
  #filter(annualRate > 0) %>%
  mutate(annualRate = ifelse(annualRate == 0, 0.05, annualRate)) %>%
  ggplot(., aes( x = log(annualRate)))+
  geom_histogram()+
  #geom_density()+
  facet_wrap(~action, scales = 'free')+
  xlab("N times per year")+
  xlim(-3.5, 8.5)


# df.tidy %>%
#   filter(annualRate > 0 ) %>%
#   ggplot(., aes( x = log(annualRate)))+
#   #geom_histogram()+
#   geom_density()+
#   facet_wrap(~action, scales = 'free')+
#   xlim(-2, 8.5)
# 
# ggsave("~/Desktop/habpriors_ff.pdf", width = 12, height = 8)
```

# Friends and family 3

### Results

```{r}
df3 <- read.csv(paste(project.path, "data/habituals/priors/friends-and-family-3-trials.csv", sep= ""))
```

How participants filled out each item? (Each participant did 15 items, randomly selected from 27)
```{r}
tab.items <- table(unique(
  df3 %>% 
    select(workerid, action)
)$action)

df.items <- data.frame(tab.items)

df.items[order(df.items$Freq),] %>% kable()
```


```{r}
df3.allZeros <- df3 %>%
  filter(person != "hypothetical") %>%
  group_by(workerid, action) %>%
  summarize(counts = sum(n_times)) %>%
  mutate(zeros = ifelse(counts == 0, 1, 0)) %>% 
  ungroup() %>%
  group_by(action) %>%
  summarize(n = n(),
            allZeros = sum(zeros)) %>%
  ungroup() %>%
  mutate(action = factor(action, levels = action[order(allZeros)]),
         knowSomebody = n - allZeros) 

ggplot(df3.allZeros %>% gather(key, val, knowSomebody, allZeros), 
       aes(x = action, y = val, fill = key))+
  geom_bar(stat = 'identity')+
  theme(axis.text.x = element_text(angle = 90))+
  scale_fill_solarized()+
  coord_flip()
```
```{r allZeros3}
df3.hypotheticals <- 
  left_join(
    df3 %>%
      filter(person != "hypothetical") %>%
      group_by(workerid, action) %>%
      summarize(counts = sum(n_times)) %>%
      filter(counts == 0) %>%
      ungroup(),
    df3 %>%
      filter(person == "hypothetical") %>%
      select(workerid, action, person)
  ) %>%
  mutate(hypothetical = ifelse(is.na(person), 0, 1)) %>%
  group_by(action) %>%
  summarize(nZeros = n(),
            nHypotheticals = sum(hypothetical)) %>%
  mutate(action = factor(action, levels = action[order(nZeros)]),
         noHypothetical = nZeros - nHypotheticals) %>%
  gather(key, val, noHypothetical, nHypotheticals)

ggplot(df3.hypotheticals, aes(x = action, y = val, fill = key)) +
  geom_bar(stat = 'identity', color = 'black') +
  theme(axis.text.x = element_text(angle = 90)) +
  coord_flip() +
  scale_fill_solarized()
```

```{r fig.height = 8, fig.width = 7}
annualRates = list("5 years" = 1/5, "2 years" = 1/2,
                   "year" = 1, "6 months" = 2, "2 months" = 6,
                   "month" = 12, "2 weeks" = 26 ,"week" = 52)

df3.tidy <- df3 %>%
  rowwise() %>%
  mutate(annualRate = annualRates[[as.character(interval)]]*n_times)


df3.tidy %>%
  #filter(annualRate > 0) %>%
  mutate(annualRate = ifelse(annualRate == 0, 0.05, annualRate)) %>%
  ggplot(., aes( x = log(annualRate)))+
  #ggplot(., aes( x = annualRate))+
  geom_histogram()+
  #geom_density()+
  facet_wrap(~action, scales = 'free')+
  xlab("N times per year")+
  xlim(-3, 9)


```

```{r fig.height = 8, fig.width = 10}
df.tidy.13 <- bind_rows(
  df.tidy %>% 
    mutate(src = 'future'),
  df3.tidy %>% 
    mutate(src = 'past')
  ) %>%
    mutate(annualRate = ifelse(annualRate == 0, 0.05, annualRate),
           logAnnual  = log(annualRate))


ggplot(df.tidy.13, aes( x = logAnnual, lty = src, color = src) ) +
  stat_ecdf()+
  facet_wrap(~action, nrow = 4)+
  scale_color_solarized()+
  scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
  theme(strip.text.y = element_text(angle = 0))

```



# Interpretation (listener) data

```{r}
df.int <- read.csv(
  paste(project.path,
        "data/habituals/interpretation/habituals-interpretation-1-trials.csv", 
        sep= ""))
```


```{r fig.height = 8, fig.width = 7}
annualRates = list("5 years" = 1/5, "2 years" = 1/2,
                   "year" = 1, "6 months" = 2, "2 months" = 6,
                   "month" = 12, "2 weeks" = 26 ,"week" = 52)

df.int.tidy <- df.int %>%
  rowwise() %>%
  mutate(annualRate = annualRates[[as.character(interval)]]*n_times)


df.int.tidy %>%
  #filter(annualRate > 0) %>%
  mutate(annualRate = ifelse(annualRate == 0, 0.05, annualRate)) %>%
  ggplot(., aes( x = log(annualRate)))+
  #ggplot(., aes( x = annualRate))+
  geom_histogram()+
  #geom_density()+
  facet_wrap(~habitual, scales = 'free')+
  xlab("N times per year")+
  xlim(-3, 9)

```


```{r fig.height = 8, fig.width = 10}
df.tidy.1.int <- bind_rows(
  df.tidy %>% 
    mutate(src = 'prior'),
  df.int.tidy %>% rename(person = characterName, action = habitual) %>%
    select(-trial_type, -characterGender, -category) %>%
    mutate(src = 'posterior')
  ) %>%
    mutate(annualRate = ifelse(annualRate == 0, 0.05, annualRate),
           logAnnual  = log(annualRate))


ggplot(df.tidy.1.int, aes( x = logAnnual, lty = src, color = src) ) +
  stat_ecdf()+
  facet_wrap(~action, nrow = 4)+
  scale_color_solarized()+
  scale_y_continuous(limits = c(0,1), breaks = c(0, 0.5, 1)) +
  theme(strip.text.y = element_text(angle = 0))
```

